Estimating individual subjective values of emotion regulation strategies

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added BIS-11

*Baratt Impulsiveness Scale.*

>>>>

*Barratt Impulsiveness Scale.*
As a third measure of self-control, the Barratt Impulsiveness Scale (BIS-11)[@Patton1995; @Hartmann2011] was used.
Responses to each item (e.g., "I am self-controlled.", recoded) are assessed on a 4-point scale ranging from 1 (never/rarely) to 4 (almost always/always).
An internal consistency of Cronbach's $\alpha=.74$ and a retest reliability of $r_{tt}=.56$ for General Impulsiveness and $r_{tt}=.66$ for Total Score across 6 month were reported [@Hartmann2011].
